Capsule Based Aspect Extraction

### 2020-05-30 paper/main.tex
updated paper

\begin{table}[tbh!]
\begin{center}
\begin{tabular}[t]{l|l|l}
\hline
 Inferred Aspects & Representative Words & Gold Aspects \\
\hline
todo & todo & todo  \\
\hline
\end{tabular}
\caption{List of inferred aspects for restaurant reviews (left), with top representative words for each inferred aspect (middle), and the corresponding gold-standard aspect labels (right). Inferred aspect labels (left) were assigned manually.}
\label{tab:aspects}
\end{center}
\end{table}

>>>>

\begin{table}[tbh!]
\begin{center}
\begin{tabular}[t]{l|l}
\hline
Representative Words & Aspects \\
\hline
chicken potato onion tomato sauce & food  \\
highly grilled seared roasted shrimp & food  \\
pay money leave didn order & price  \\
minute asked manager seated waiter & staff  \\
wall room space ceiling lit & ambience  \\
dish menu entree course flavor & food  \\
birthday saturday reservation friend friday & anecdotes  \\
year ny experience life nyc & miscellaneous  \\
service staff waitstaff attentive friendly & staff  \\
month time minute week hour & miscellaneous  \\
drink wine sangria nice perfect & food  \\
gras crust rib pork foie & food  \\
chocolate butter fruit sauce sweet & food  \\
chinese japanese american mexican indian & food  \\
\hline
\end{tabular}
\caption{List of top representative words for each aspect (left), and aspect labels (right). Aspect labels (right) were assigned manually.}
\label{tab:aspects}
\end{center}
\end{table}
